---
title: "R Notebook for the cystectomy study"
author: "Pascal Jerney"
date: "Created 2nd May 2020"
output:
  bookdown::gitbook: default
  html_notebook: default
  pdf_document: default
---

```{r setup, echo=FALSE}
# Load packages ----
if (!require("pacman")) {
  install.packages("pacman")
}
pacman::p_load(
  "tidyverse",
  "here",
  "fs",
  "tableone",
  "modelr",
  "tidybayes",
  "gridExtra",
  "sjPlot",
  "htmltools"
)

# Set working directory ----
knitr::opts_knit$set(root.dir = here::here())

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dev = "png",
  dpi = 150,
  fig.asp = 0.8,
  fig.width = 10,
  out.width = "100%",
  fig.align = "center"
)

```

```{r load_data, echo=FALSE,cache=FALSE}
# Load data from 0_get_and_tidy_data ----
tibble.oak_bleeding_tidy <-
  read_rds(path = path(
    'empirical',
    '2_pipeline',
    '0_get_and_tidy_data',
    'out',
    'oak_bleeding_tidy',
    ext = 'rds'
  ))

# Filter patients with surgery before 2000 ----
tibble.oak_bleeding_tidy <-
  tibble.oak_bleeding_tidy %>%
  filter(op_year >= 2000)

# Load models from 1_generate_models ----
model.intraoptransfusion_bloodlosspercent_preophb_year <-
  read_rds(path = path(
    'empirical',
    '2_pipeline',
    '1_generate_models',
    'out',
    'intraoptransfusion_bloodlosspercent_preophb_year',
    ext = 'rds'
  ))
```

# Prerequisites

## Formulas

  - Indexed blood volume^[Lemmens, H. J. M., Bernstein, D. P., & Brodsky, J. B. (2006). Estimating blood volume in obese and morbidly obese patients. Obesity Surgery, 16(6), 773–776. https://doi.org/10.1381/096089206777346673]: $BV_i = \frac{70}{\sqrt{\frac{BMI}{22}}}$^[$BV_i$ = Indexed blood volume, $BMI$ = Body mass index]
  - Estimated blood volume: $BV_e = BV_i * Weight$^[$BV_e$ = Estimated blood volume]
  - Blood loss ratio: $BL_r = \frac{BV_e}{BL_a}$^[$BL_r$ = Blood loss ratio, $BL_a$ = Absolute blood loss]

# Results

## Data plots

```{r data_plots,echo=FALSE}
qqplot_bloodlossratio <-
  tibble.oak_bleeding_tidy %>%
  drop_na(blood_loss_ratio) %>%
  ggplot(aes(sample = blood_loss_ratio)) +
  geom_qq() +
  geom_qq_line() +
  labs(title = "Q-Q-Plot for blood loss ratio", subtitle = "Normal scale", x = "Theoretical quantiles", y = "Sample quantiles") +
  theme_light()

qqplot_logbloodlossratio <-
  tibble.oak_bleeding_tidy %>%
  drop_na(blood_loss_ratio) %>%
  ggplot(aes(sample = log(blood_loss_ratio))) +
  geom_qq() +
  geom_qq_line() +
  labs(title = "Q-Q-Plot for blood loss ratio", subtitle = "Natural logarithm scale", x = "Theoretical quantiles", y = "Sample quantiles") +
  theme_light()

grid.arrange(qqplot_bloodlossratio, qqplot_logbloodlossratio, ncol = 2)

tibble.oak_bleeding_tidy %>%
drop_na(blood_loss_ratio) %>%
ggplot(aes(x = blood_loss_ratio)) +
geom_histogram(binwidth = 0.05) +
labs(title = "Histogram of blood loss ratio", x = "Blood loss ratio", y = "Count") +
theme_light()

tibble.oak_bleeding_tidy %>%
drop_na(intraop_transfusion) %>%
ggplot(aes(x = intraop_transfusion)) +
geom_bar() +
labs(title = "Bar chart of intraoperative transfusion", x = "Intraoperative transfusion", y = "Count") +
theme_light()
```

## Model outputs

Model with intraoperative transfusion as predictor, blood loss percentage and preoperative hemoglobin as population-level effects and operation year as group-level effect.

```{r model_tables,echo=FALSE,results="asis"}
model1 <- tab_model(model.intraoptransfusion_bloodlosspercent_preophb_year, rm.terms = c("Intercept"), pred.labels = c(blood_loss_percent = "Percent blood loss", preop_hb = "Preoperative hemoglobin"), dv.labels = c("Intraoperative transfusion"), show.ci = 0.999, use.viewer = FALSE)
cat(model1$knitr)
```

## Model plots

```{r model_plots,echo=FALSE}
tibble.oak_bleeding_tidy %>%
data_grid(blood_loss_percent = seq_range(blood_loss_percent, by = 1, pretty = TRUE), preop_hb = seq_range(preop_hb, by = 20, pretty = TRUE)) %>%
add_linpred_draws(model.intraoptransfusion_bloodlosspercent_preophb_year, re_formula = NA) %>%
median_hdci(.width = c(0.95, 0.999)) %>%
ggplot(aes(x = blood_loss_percent, y = .value)) +
facet_wrap(vars(preop_hb)) +
geom_lineribbon() +
labs(title = str_wrap("Probability for transfusion depending on preoperative hemoglobin and blood loss percentage", 100), subtitle = "Preoperative Hb", x = "Blood loss ratio", y = "Probability for transfusion") +
coord_cartesian(xlim = c(0, 100)) +
theme_light()
```