---
title: "R Notebook for the cystectomy study"
author: "Pascal Jerney"
date: "3rd May 2020"
output:
  bookdown::gitbook:
    config:
      toc:
        collapse: subsection
        scroll_highlight: yes
        before: null
        after: null
      toolbar:
        position: fixed
      edit : null
      download: ["notebook_cystectomy.pdf", "notebook_cystectomy.epub"]
      search: yes
      fontsettings:
        theme: white
        family: sans
        size: 2
      sharing:
        facebook: yes
        github: no
        twitter: yes
        linkedin: no
        weibo: no
        instapaper: no
        vk: no
        all: ['facebook', 'twitter', 'linkedin', 'weibo', 'instapaper']
      info: yes
  html_notebook: default
  pdf_document: default
---

```{r setup, echo=FALSE}
# Load packages ----
if (!require("pacman")) {
  install.packages("pacman")
}
pacman::p_load(
  "tidyverse",
  "rprojroot",
  "fs",
  "tableone",
  "modelr",
  "glue",
  "tidybayes",
  "gridExtra",
  "sjPlot",
  "htmltools",
  "brms",
  "bayestestR",
  "ROCR"
)

# Set working directory ----
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dev = "png",
  dpi = 300,
  fig.asp = 0.8,
  fig.width = 10,
  out.width = "100%",
  fig.align = "center"
)

```

```{r load_data, echo=FALSE,cache=FALSE}
setwd(here::here())

# Load data from 0_get_and_tidy_data ----
tibble.oak_bleeding_tidy <-
  read_rds(path = path_wd(
    'empirical',
    '2_pipeline',
    '0_get_and_tidy_data',
    'out',
    'oak_bleeding_tidy',
    ext = 'rds'
  ))

## Set up helpers ----
helper.drop_na <-
  read_rds(path = path_wd(
    'empirical',
    '2_pipeline',
    '0_create_helpers',
    'out',
    'drop_na',
    ext = 'rds'
  ))

## Filter patients ----
tibble.oak_bleeding_model <-
  tibble.oak_bleeding_tidy %>%
  filter(op_year >= 2000) %>% # surgery before 2000
  filter(bmi >= 12) %>% # bmi less than 12
  drop_na(all_of(helper.drop_na)) # drop NA values in selected columns

# Load models from 1_generate_multivar_models ----
models.intraoptransfusion_multivar <-
  read_rds(path = path_wd(
    'empirical',
    '2_pipeline',
    '1_generate_multivar_models',
    'out',
    'intraoptransfusion_multivar',
    ext = 'rds'
  ))

```

# Index

Welcome to the notebook!

# Prerequisites

## Formulas

  - Indexed blood volume^[Lemmens, H. J. M., Bernstein, D. P., & Brodsky, J. B. (2006). Estimating blood volume in obese and morbidly obese patients. Obesity Surgery, 16(6), 773–776. https://doi.org/10.1381/096089206777346673]: $BV_i = \frac{70}{\sqrt{\frac{BMI}{22}}}$^[$BV_i$ = Indexed blood volume, $BMI$ = Body mass index]
  - Estimated blood volume: $BV_e = BV_i \cdot Weight$^[$BV_e$ = Estimated blood volume]
  - Blood loss ratio: $BL_r = \frac{BV_e}{BL_a}$^[$BL_r$ = Blood loss ratio, $BL_a$ = Absolute blood loss]
  - Standardization method for age and bmi^[Iglewicz, B., & Hoaglin, D. C. (1993). How to detect and handle outliers. Milwaukee, Wis: ASQC Quality Press.]: $M_i = \frac{0.6745(x_i - \tilde(x))}{2 \cdot MAD}$^[$M_i$ = Modified Z-score, $\tilde(x)$ = Median of $x$, $MAD$ = Median absolute deviation]

# Results

## Data plots

```{r data_plots,echo=FALSE}
qqplot_bloodlossratio <-
  tibble.oak_bleeding_tidy %>%
  drop_na(blood_loss_ratio) %>%
  ggplot(aes(sample = blood_loss_ratio)) +
  geom_qq() +
  geom_qq_line() +
  labs(title = "Q-Q-Plot for blood loss ratio", subtitle = "Normal scale", x = "Theoretical quantiles", y = "Sample quantiles") +
  theme_light()

qqplot_logbloodlossratio <-
  tibble.oak_bleeding_tidy %>%
  drop_na(blood_loss_ratio) %>%
  ggplot(aes(sample = log(blood_loss_ratio))) +
  geom_qq() +
  geom_qq_line() +
  labs(title = "Q-Q-Plot for blood loss ratio", subtitle = "Natural logarithm scale", x = "Theoretical quantiles", y = "Sample quantiles") +
  theme_light()

grid.arrange(qqplot_bloodlossratio, qqplot_logbloodlossratio, ncol = 2)

tibble.oak_bleeding_tidy %>%
drop_na(blood_loss_ratio) %>%
ggplot(aes(x = blood_loss_ratio)) +
geom_histogram(binwidth = 0.05) +
labs(title = "Histogram of blood loss ratio", x = "Blood loss ratio", y = "Count") +
theme_light()

tibble.oak_bleeding_tidy %>%
drop_na(intraop_transfusion) %>%
ggplot(aes(x = intraop_transfusion)) +
geom_bar() +
labs(title = "Bar chart of intraoperative transfusion", x = "Intraoperative transfusion", y = "Count") +
theme_light()
```

## Model outputs

### Models with intraoperative transfusion as response

#### Full model

```{r model1full,echo=FALSE}
model1_full <- models.intraoptransfusion_multivar[[1]]
```

##### Model diagnostics

```{r model1full_diagnostics,echo=FALSE}
mcmc_plot(model1_full, type = "trace")
mcmc_plot(model1_full, type = "intervals") + geom_vline(aes(xintercept = 0))
```

##### Posterior predictive check plot

```{r model1full_ppcheck,echo=FALSE}
pp_check(model1_full, nsamples = 10)
```

##### Coefficients table

```{r model1full_table,echo=FALSE,results="asis"}
tab_model(
  model1_full,
  rm.terms = c("Intercept"),
  pred.labels = c(
    blood_loss_percent = "Percent blood loss",
    preop_hb = "Preoperative hemoglobin"
  ),
  dv.labels = c("Intraoperative transfusion"),
  show.ci = 0.95,
  use.viewer = FALSE
) %>%
.$knitr %>%
cat(.)
```

##### Maximum a posteriori p-values

```{r model1full_pmap,echo=FALSE}
p_map(model1_full) %>%
as_tibble() %>%
arrange(p_MAP) %>%
knitr::kable()
```

##### Region of practical equivalence

Using a ROPE range of -0.055 to 0.055 ($0.1 \cdot \frac{\sqrt{3}}{\pi}$) and a CI of 1.

```{r model1full_rope,echo=FALSE}
percentage_in_rope <-
  rope(
    model1_full,
    range = c(-0.055, 0.055),
    ci = 1
  )
plot(percentage_in_rope)
```

##### ROC-AUC

```{r model1full_rocauc,echo=FALSE}
predictions <-
  tibble.oak_bleeding_model %>%
  select(all_of(helper.drop_na)) %>%
  add_linpred_draws(model1_full, re_formula = NA) %>%
  median_hdci()

roc.pred <-
  prediction(
    predictions = predictions %>% pull(.value),
    labels = predictions %>% pull(intraop_transfusion)
  )

roc.auc <-
  performance(
    roc.pred,
    measure = "auc"
  )

cat(glue("AUC: ", roc.auc@y.values[[1]]))

roc.tpr_fpr <-
  performance(
    roc.pred,
    measure = "tpr",
    x.measure = "fpr"
  )

plot(
  roc.tpr_fpr,
  main = "ROC-AUC"
)

```

##### Conditional probability plot

```{r model1full_conditional_plot,echo=FALSE}
# tibble.oak_bleeding_tidy %>%
# data_grid(blood_loss_percent = seq_range(blood_loss_percent, by = 1, pretty = TRUE), preop_hb = seq_range(preop_hb, by = 20, pretty = TRUE)) %>%
# add_linpred_draws(model.intraoptransfusion_bloodlosspercent_preophb_opyear, re_formula = NA) %>%
# median_hdci(.width = c(0.95, 0.999)) %>%
# ggplot(aes(x = blood_loss_percent, y = .value)) +
# facet_wrap(vars(preop_hb)) +
# geom_lineribbon() +
# labs(title = str_wrap("Probability for transfusion depending on preoperative hemoglobin and blood loss percentage", 100), subtitle = "Preoperative Hb", x = "Blood loss percent", y = "Probability for transfusion") +
# coord_cartesian(xlim = c(0, 100)) +
# theme_light()
```

#### Reduced model

```{r model1reduced,echo=FALSE}
model1_reduced <- models.intraoptransfusion_multivar[[2]]
```

##### Model diagnostics

```{r model1reduced_diagnostics,echo=FALSE}
mcmc_plot(model1_reduced, type = "trace")
mcmc_plot(model1_reduced, type = "intervals") + geom_vline(aes(xintercept = 0))
```

##### Posterior predictive check plot

```{r model1reduced_ppcheck,echo=FALSE}
pp_check(model1_reduced, nsamples = 10)
```

##### Coefficients table

```{r model1reduced_table,echo=FALSE,results="asis"}
tab_model(
  model1_reduced,
  rm.terms = c("Intercept"),
  pred.labels = c(
    blood_loss_percent = "Percent blood loss",
    preop_hb = "Preoperative hemoglobin"
  ),
  dv.labels = c("Intraoperative transfusion"),
  show.ci = 0.95,
  use.viewer = FALSE
) %>%
.$knitr %>%
cat(.)
```

##### Maximum a posteriori p-values

```{r model1reduced_pmap,echo=FALSE}
p_map(model1_reduced) %>%
as_tibble() %>%
arrange(p_MAP) %>%
knitr::kable()
```

##### Region of practical equivalence

Using a ROPE range of -0.055 to 0.055 ($0.1 \cdot \frac{\sqrt{3}}{\pi}$) and a CI of 1.

```{r model1reduced_rope,echo=FALSE}
percentage_in_rope <-
  rope(
    model1_reduced,
    range = c(-0.055, 0.055),
    ci = 1
  )
plot(percentage_in_rope)
```

##### ROC-AUC

```{r model1reduced_rocauc,echo=FALSE}
predictions <-
  tibble.oak_bleeding_model %>%
  select(all_of(helper.drop_na)) %>%
  add_linpred_draws(model1_reduced, re_formula = NA) %>%
  median_hdci()

roc.pred <-
  prediction(
    predictions = predictions %>% pull(.value),
    labels = predictions %>% pull(intraop_transfusion)
  )

roc.auc <-
  performance(
    roc.pred,
    measure = "auc"
  )

cat(glue("AUC: ", roc.auc@y.values[[1]]))

roc.tpr_fpr <-
  performance(
    roc.pred,
    measure = "tpr",
    x.measure = "fpr"
  )

plot(
  roc.tpr_fpr,
  main = "ROC-AUC"
)

```

##### Conditional probability plot

```{r model1reduced_conditional_plot,echo=FALSE}
# tibble.oak_bleeding_tidy %>%
# data_grid(blood_loss_percent = seq_range(blood_loss_percent, by = 1, pretty = TRUE), preop_hb = seq_range(preop_hb, by = 20, pretty = TRUE)) %>%
# add_linpred_draws(model.intraoptransfusion_bloodlosspercent_preophb_opyear, re_formula = NA) %>%
# median_hdci(.width = c(0.95, 0.999)) %>%
# ggplot(aes(x = blood_loss_percent, y = .value)) +
# facet_wrap(vars(preop_hb)) +
# geom_lineribbon() +
# labs(title = str_wrap("Probability for transfusion depending on preoperative hemoglobin and blood loss percentage", 100), subtitle = "Preoperative Hb", x = "Blood loss percent", y = "Probability for transfusion") +
# coord_cartesian(xlim = c(0, 100)) +
# theme_light()
```
